---
title: "banffIT-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{banffIT-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The banffIT package provides functions to assign standardized diagnoses 
using the Banff Classification (Category 1 to 6 diagnoses, including Acute 
and Chronic active T-cell mediated rejection as well as Active, 
Chronic active, and Chronic antibody mediated rejection). The main function 
`banff_launcher()`considers a minimal dataset containing biopsies information 
in a specific format (described by a data dictionary), verifies its content and 
format (based on the data dictionary), assign diagnoses, and create a summary 
report.

# Get started

## Install the package and use the example file

This command example runs the diagnosis assignment process on the dataset 
specified in the input_file path. The output files will be saved in
path_folder/example. The diagnoses will be displayed in English and only 
observation with adequacy == 1 will be taken into consideration due to the 
option_filter argument. Finally, the output dataset will contain variables 
generated in the process due to the argument "detail" set to TRUE.

```{r, eval=FALSE}

# To install banffIT
install.packages('banffIT')

library(banffIT)
# If you need help with the package, please use:
banffIT_website()

# use example
input_file = system.file("extdata", "example.xlsx", package = "banffIT")
banff_launcher(
  input_file = input_file,
  output_folder = 'folder_path/example',
  language = 'label:en',
  option_filter = adequacy == 1,
  detail = TRUE)

```
