---
title: "banffIT-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{banffIT-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The banffIT package provides provides functions to assign standardized diagnosis 
using the Banff Classification (Category 1 to 6 diagnoses, including Acute 
and Chronic active T-cell mediated rejection as well as Active, 
Chronic active, and Chronic antibody mediated rejection). The main function 
[banff_launcher()](https://PersonalizedTransplantCare.github.io/banffIT-documentation/reference/banff_launcher.html)
considers a minimal dataset containing biopsies information in a specific 
format (described by a data dictionary), verifies its content and format 
(based on the data dictionary), assign diagnoses, and create a summary 
report.

# Get started

## Install the package and use the example file

```{r, eval=FALSE}
# To install banffIT:
install.packages('banffIT')

library(banffIT)
# If you need help with the package, please use:
banffIT_website()

# use the example file provided. remplace tempdir by a directory name.
banff_file <- system.file("extdata", "example.xlsx", package = "banffIT")
banff_launcher(banff_file, output_folder = tempdir())

```
